Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area" \\ [1ex] \large Supplementary Information

### 2022-02-13 paper/main.tex
remove links to github from references

\documentclass[english,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage{babel}
\usepackage[section]{placeins}
\usepackage{flafter}
\usepackage{comment}
\usepackage{breakurl}
\usepackage{svg}
\usepackage[labelfont=bf,font=small]{caption}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm,includeheadfoot]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
%\setlength{\headheight}{40pt}
%\lhead{\textsc{\scidatalogo}}
\usepackage[comma,super,sort&compress]{natbib}
\usepackage{xr}
\externaldocument{suppl}
% \usepackage{helvet}

% \renewcommand{\familydefault}{\sfdefault}

@@

% open question
In this study, we investigate whether increased hemodynamic activity in the PPA
that is usually detected by contrasting blocks of pictures is also present under
more natural conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both
\textit{visual and auditory} spatial information using two naturalistic stimuli
(\citep[see reviews][]{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic}).
% AV stimulus
The current operationalization of visual spatial perception is based on an
annotation of cuts and depicted locations in the audio-visual movie ``Forrest
Gump'' \citep{haeusler2016cutanno}, while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech occurring in the movie's audio-description
\citep{haeusler2021studyforrest}.
% pictures -> movie -> audio-description
The movie stimulus shares the stimulation in the visual domain with classical
localizer stimuli, while featuring real-life-like visual complexity and
naturalistic auditory stimulation. The audio-description maintains the
naturalistic nature of the movie stimulus, but limited to the auditory domain.
% current GLM contrasts
We applied model-based, mass-univariate analyses to BOLD fMRI data from both
naturalistic stimuli \citep{hanke2016simultaneous, hanke2014audiomovie},
available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org} \citep{hanke2016aligned}.
% comparison to previous GLM
We compare current results to results of a previously performed model-based,
mass-univariate analysis that was applied to data from a conventional functional
localizer performed with the same set of participants
\citep{sengupta2016extension, sengupta2016extensiondata}.
% intro to hypo a
Similarly to the functional localizer, we currently also capitalize on events
that ought to evoke the cognitive processing of spatial information.
% hypo a
Thus, we hypothesized that our whole-brain analyses would reveal increased
hemodynamic activity in medial temporal regions that were functionally
identified as the PPA by the analysis of the localizer data.
%hypo b: individuals
We hypothesized further that a purely auditory stimulus could, in principle,
localize the PPA as an example of a ``visual area'' in individual persons,
% application in individuals
and may offer an alternative paradigm to assess brain functions in visually
impaired individuals.

@@

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlates with increased hemodynamic activity in the PPA.
%
Based on an annotation of cuts in the movie and an annotation of speech spoken
by the audio-description's narrator, we selected events in both stimuli that
should correlate with the perception of spatial information and contrasted them
with events that should correlate with non-spatial
perception to a lesser degree, or not at all (see Table~\ref{tab:events}).
% from supplementals
In order to test the robustness of our approach, we created multiple linear
model (GLM) $t$-contrasts for the movie and audio-description (see
Table~\ref{tab:contrasts}).
% subjectively assessed balance
For each stimulus, we chose a primary contrast for result presentation
based on a subjectively assessed balance of how
well the averaged events within categories represent spatial and non-spatial
information, and the number of events in the stimulus.
% group level
On a group average level, we report results from whole-brain analyses of
the movie's and the audio-description's primary contrasts and compare these
results to a traditional visual localizer \citep{sengupta2016extension}.
% individual level
For each individual, we also compare the activation pattern from naturalistic
auditory stimulation to the individual PPA localization with a block-design
stimulus.
% reference to supplementals
An evaluation of the results' robustness across all created contrasts on a group
average level is provided in the Supplementary Information (see
Figure~\ref{fig:stability-slices-volsurf}).
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group average level as well as
individual results of the primary $t$-contrasts co-registered to the
group-template (MNI152 space) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

@@

% data sources
The current analyses were carried out on the same preprocessed fMRI data
\citep{hanke2016aligned} that were used for the technical validation analysis
presented in \citet{hanke2016simultaneous}.
% exclusion of VP 10
Of those 15 participants in the studyforrest dataset that took part in all three
experiments, data of one participant were dropped due to invalid distortion
correction during scanning of the audio-description stimulus.
% preprocessing of pre-aligned data
Data were corrected for motion, aligned with and re-sliced onto a
participant-specific BOLD template image \citep{sengupta2016extension} (uniform
spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
audio-description and movie data).
% preprocessing intro
Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool
\citep{woolrich2001autocorr}) as shipped with FSL v5.0.9
(\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library}
\citep{smith2004fsl}) on a computer-cluster running
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

% new; PPA analysis
All fMRI data, annotations, and results are available as Datalad \citep{datalad}
datasets, published to or linked from the \emph{G-Node GIN} repository
(\href{https://doi.org/10.12751/g-node.7is9s6}{\url{doi.org/10.12751/g-node.qmevq0}}\citep{haeusler2021ppa}).
% original
Raw data of the audio-description, movie and visual localizer were originally
published on the \emph{OpenfMRI} portal
(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113},
\url{https://legacy.openfmri.org/dataset/ds000113d}\citep{hanke2016ds000113d}).
% visual localizer
Results from the localization of higher visual areas are available as Datalad
datasets at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-visualrois}{\url{github.com/psychoinformatics-de/studyforrest-data-visualrois}}\citep{sengupta2016extensiondata}).
% raw data
The realigned participant-specific timeseries that were used in the current
analyses were derived from the raw data releases and are available as Datalad
datasets at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}
\citep{hanke2016aligned}).
% cut annotation
The annotation of cuts is available at \emph{F1000Research}
(\href{https://doi.org/10.5256/f1000research.9536.d134823}{\url{doi.org/10.5256/f1000research.9536.d134823}}
\citep{haeusler2016cutdata}),
% speech annotation
the annotation of speech is available at \emph{OSF}
(\href{https://doi.org/10.17605/OSF.IO/F5J3E}{\url{doi.org/10.17605/OSF.IO/F5J3E}}
\citep{haeusler2020speechdata}).
% surface data
Participant-specific reconstructed cortical surface are available as Datalad
dataset at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer}{\url{github.com/psychoinformatics-de/studyforrest-data-freesurfer}}
\citep{hanke2016freesurferdata}), and are also part of the original data release
on \emph{OpenfMRI}
(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113}.

>>>>

\documentclass[english,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage{babel}
\usepackage[section]{placeins}
\usepackage{flafter}
\usepackage{comment}
\usepackage{svg}
\usepackage[labelfont=bf,font=small]{caption}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm,includeheadfoot]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
%t\usepackage{breakurl}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
%\setlength{\headheight}{40pt}
%\lhead{\textsc{\scidatalogo}}
\usepackage[comma,super,sort&compress]{natbib}
\usepackage{xr}
\externaldocument{suppl}
% \usepackage{helvet}

\newcommand{\cmmnt}[1]{\ignorespaces}
% \renewcommand{\familydefault}{\sfdefault}

@@

% open question
In this study, we investigate whether increased hemodynamic activity in the PPA
that is usually detected by contrasting blocks of pictures is also present under
more natural conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both
\textit{visual and auditory} spatial information using two naturalistic stimuli
(\citep[see reviews][]{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic}).
% AV stimulus
The current operationalization of visual spatial perception is based on an
annotation of cuts and depicted locations in the audio-visual movie ``Forrest
Gump'' \citep{haeusler2016cutanno}, while
% AD stimulus
the operationalization of non-visual spatial perception is based on an
annotation of speech occurring in the movie's audio-description
\citep{haeusler2021studyforrest}.
% pictures -> movie -> audio-description
The movie stimulus shares the stimulation in the visual domain with classical
localizer stimuli, while featuring real-life-like visual complexity and
naturalistic auditory stimulation. The audio-description maintains the
naturalistic nature of the movie stimulus, but limited to the auditory domain.
% current GLM contrasts
We applied model-based, mass-univariate analyses to BOLD fMRI data from both
naturalistic stimuli \citep{hanke2016simultaneous, hanke2014audiomovie},
available from the open-data resource
\href{http://www.studyforrest.org}{studyforrest.org}.
% comparison to previous GLM
We compare current results to results of a previously performed model-based,
mass-univariate analysis that was applied to data from a conventional functional
localizer performed with the same set of participants
\citep{sengupta2016extension}.
% intro to hypo a
Similarly to the functional localizer, we currently also capitalize on events
that ought to evoke the cognitive processing of spatial information.
% hypo a
Thus, we hypothesized that our whole-brain analyses would reveal increased
hemodynamic activity in medial temporal regions that were functionally
identified as the PPA by the analysis of the localizer data.
%hypo b: individuals
We hypothesized further that a purely auditory stimulus could, in principle,
localize the PPA as an example of a ``visual area'' in individual persons,
% application in individuals
and may offer an alternative paradigm to assess brain functions in visually
impaired individuals.

@@

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlates with increased hemodynamic activity in the PPA.
%
Based on an annotation of cuts in the movie and an annotation of speech spoken
by the audio-description's narrator, we selected events in both stimuli that
should correlate with the perception of spatial information and contrasted them
with events that should correlate with non-spatial perception to a lesser
degree, or not at all\cmmnt{ (see Table~\ref{tab:events})}.
% from supplementals
In order to test the robustness of our approach, we created multiple linear
model (GLM) $t$-contrasts for the movie and audio-description\cmmnt{ (see
Table~\ref{tab:contrasts})}.
% subjectively assessed balance
For each stimulus, we chose a primary contrast for result presentation based on
a subjectively assessed balance of how well the averaged events within
categories represent spatial and non-spatial information, and the number of
events in the stimulus.
% group level
On a group average level, we report results from whole-brain analyses of the
movie's and the audio-description's primary contrasts and compare these results
to a traditional visual localizer \citep{sengupta2016extension}.
% individual level
For each individual, we also compare the activation pattern from naturalistic
auditory stimulation to the individual PPA localization with a block-design
stimulus.
% reference to supplementals
An evaluation of the results' robustness across all created contrasts on a group
average level is provided in the Supplementary Information (see
Figure~\ref{fig:stability-slices-volsurf}).
% NeuroVault
Unthresholded $Z$-maps of all contrasts on a group average level as well as
individual results of the primary $t$-contrasts co-registered to the
group-template (MNI152 space) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{\url{neurovault.org/collections/KADGMGVZ}}.

@@

% data sources
The current analyses were carried out on the same preprocessed fMRI data (s.
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}) that were used for the technical validation analysis presented in
\citet{hanke2016simultaneous}.
% exclusion of VP 10
Of those 15 participants in the studyforrest dataset that took part in all three
experiments, data of one participant were dropped due to invalid distortion
correction during scanning of the audio-description stimulus.
% preprocessing of pre-aligned data
Data were corrected for motion, aligned with and re-sliced onto a
participant-specific BOLD template image \citep{sengupta2016extension} (uniform
spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
audio-description and movie data).
% preprocessing intro
Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool
\citep{woolrich2001autocorr}) as shipped with FSL v5.0.9
(\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library}
\citep{smith2004fsl}) on a computer-cluster running
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

% new; PPA analysis
All fMRI data, annotations, and results are available as Datalad \citep{datalad}
datasets, published to or linked from the \emph{G-Node GIN} repository
(\href{https://doi.org/10.12751/g-node.7is9s6}{\url{doi.org/10.12751/g-node.qmevq0}}\citep{haeusler2021ppa}).
% original
Raw data of the audio-description, movie and visual localizer were originally
published on the \emph{OpenfMRI} portal
(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113},
\space \url{https://legacy.openfmri.org/dataset/ds000113d}\citep{hanke2016ds000113d}).
% visual localizer
Results from the localization of higher visual areas are available as Datalad
datasets at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-visualrois}{\url{github.com/psychoinformatics-de/studyforrest-data-visualrois}}).
% raw data
The realigned participant-specific timeseries that were used in the current
analyses were derived from the raw data releases and are available as Datalad
datasets at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{\url{github.com/psychoinformatics-de/studyforrest-data-aligned}}.
% cut annotation
The annotation of cuts is available at \emph{F1000Research}
(\href{https://doi.org/10.5256/f1000research.9536.d134823}{\url{doi.org/10.5256/f1000research.9536.d134823}}
\citep{haeusler2016cutdata}),
% speech annotation
the annotation of speech is available at \emph{OSF}
(\href{https://doi.org/10.17605/OSF.IO/F5J3E}{\url{doi.org/10.17605/OSF.IO/F5J3E}}
\citep{haeusler2020speechdata}).
% surface data
Participant-specific reconstructed cortical surface are available as Datalad
dataset at \emph{GitHub} (
\href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer}{\url{github.com/psychoinformatics-de/studyforrest-data-freesurfer}},
and are also part of the original data release on \emph{OpenfMRI}
(\url{https://legacy.openfmri.org/dataset/ds000113}\citep{Hanke2014ds000113}.

### 2022-02-13 paper/suppl.tex
remove links to github from references

\documentclass[english,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage{babel}
\usepackage[section]{placeins}
\usepackage{flafter}
\usepackage{comment}
\usepackage{breakurl}
\usepackage{svg}
\usepackage[labelfont=bf,font=small]{caption}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm,includeheadfoot]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
%\setlength{\headheight}{40pt}
%\lhead{\textsc{\scidatalogo}}
\usepackage[comma,super,sort&compress]{natbib}
\usepackage{xr}
\externaldocument{main}
\makeatletter
\renewcommand{\thefigure}{S\@arabic\c@figure}
\makeatother
% \usepackage{helvet}

@@

% individiaul results; intro
The results of the fixed-effects second-level analysis of the movie's primary
contrast (\texttt{vse\_new > vpe\_old}) and audio-description's primary contrast
(\texttt{geo, groom} > non-spatial noun categories) mapped onto subject-specific
cortical surfaces can be seen in Figure~\ref{fig:subjs_ao_av_c1_surf}.
% reconstruction
% \href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v5.3.0
\citep{dale1999cortical} was used to reconstruct surfaces from T1-weighted
images and an additional high-resolution T2-weighted image
\citep{hanke2016freesurferdata}.
% projection
Thresholded $Z$-maps ($Z$>3.4; $p$<.05, cluster-corrected) were projected onto
the cortical surfaces using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
'mri\_vol2surf' command (unthresholded $Z$-maps are provided at \href{https://neurovault.org/collections/KADGMGVZ}{\url{neurovault.org/collections/KADGMGVZ}}).
% smoothing
After projection, individual PPA ROIs were spatially smoothed by applying a
Gaussian kernel with full width at half maximum (FWHM) of \unit[2.0]{mm}.

>>>>

\documentclass[english,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage{babel}
\usepackage[section]{placeins}
\usepackage{flafter}
\usepackage{comment}
\usepackage{svg}
\usepackage[labelfont=bf,font=small]{caption}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
% \usepackage[disable]{todonotes}
\usepackage{todonotes}
\usepackage{units}
\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm,includeheadfoot]{geometry}
\usepackage[
colorlinks=true,
	citecolor=black,
  urlcolor=black,
	linkcolor=black
]{hyperref}
\usepackage{breakurl}
%\newcommand{\scidatalogo}{\includegraphics[height=36pt]{SciData_logo.jpg}}
\newcommand{\scidatalogo}{}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
%\setlength{\headheight}{40pt}
%\lhead{\textsc{\scidatalogo}}
\usepackage[comma,super,sort&compress]{natbib}
\usepackage{xr}
\externaldocument{main}
\makeatletter
\renewcommand{\thefigure}{S\@arabic\c@figure}
\makeatother
% \usepackage{helvet}

@@

% individiaul results; intro
The results of the fixed-effects second-level analysis of the movie's primary
contrast (\texttt{vse\_new > vpe\_old}) and audio-description's primary contrast
(\texttt{geo, groom} > non-spatial noun categories) mapped onto subject-specific
cortical surfaces can be seen in Figure~\ref{fig:subjs_ao_av_c1_surf}.
% reconstruction
% \href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer.git}{dataset}
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer} v5.3.0
\citep{dale1999cortical} was used to reconstruct surfaces from T1-weighted
images and an additional high-resolution T2-weighted image
% \citep{hanke2016freesurferdata}
(s. \href{https://github.com/psychoinformatics-de/studyforrest-data-freesurfer}{\url{github.com/psychoinformatics-de/studyforrest-data-freesurfer}}).
% projection
Thresholded $Z$-maps ($Z$>3.4; $p$<.05,\linebreak cluster-corrected) were projected onto
the cortical surfaces using
\href{https://surfer.nmr.mgh.harvard.edu}{FreeSurfer's} \citep{dale1999cortical}
'mri\_vol2surf' command (unthresholded $Z$-maps are provided at
\href{https://neurovault.org/collections/KADGMGVZ}{\url{neurovault.org/collections/KADGMGVZ}}).
% smoothing
After projection, individual PPA ROIs were spatially smoothed by applying a
Gaussian kernel with full width at half maximum (FWHM) of \unit[2.0]{mm}.
